---
title: "PLPA6820_CodingChallenge4"
author: "Bria Smith"
date: "2026-02-19"
output: 
  html_document:
  word_document:
  md_document:
    variant: gfm
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Article from Plant Disease](https://doi.org/10.1094/PDIS-06-21-1253-RE)

## Question 1: Explain the following

### - YAML Header: gives information on the file title, author, data, and output.My YAML header has my name, shows that I created my R markdown file today, and that it will render as a word document.

### - Literate programming: allows individuals to understand the purpose of your code and different steps by combining the programming language with daily language. 

## Question 1b: Read the data using a relative file path
```{r cars}
read.csv("MycotoxinData.csv", na.strings = "na")
```
## Question 1c: Make a separate code chunk for the figures plotting the data
### Plot 1
```{r}
Plot_1 <- ggplot(Mycotoxin, aes(x = Treatment, y = DON, color = Cultivar, fill = Cultivar)) +
  geom_boxplot() +
  geom_point(position=position_jitterdodge(dodge.width = 0.6), color = "#009E73") + # coloring points, setting jitter and jitter width
  scale_fill_manual(values=c("#F0E442", "#0072B2")) + # filling and coloring boxplots
  xlab("") + # labeling x-axis
  ylab("DON(ppm)") + # labeling y-axis
  theme_classic() + # classic theme
  facet_wrap(~Cultivar) # faceted by Cultivar
plot(Plot_1)

```
### Plot 2
```{r}
Plot_2 <- ggplot(Mycotoxin, aes(x = Treatment, y = X15ADON, color = Cultivar, fill = Cultivar)) +
  geom_boxplot() +
  geom_point(position=position_jitterdodge(dodge.width = 0.6), color = "#009E73") + # coloring points, setting jitter and jitter width
  scale_fill_manual(values=c("#F0E442", "#0072B2")) + # filling and coloring boxplots
  xlab("") + # labeling x-axis
  ylab("15ADON") + # labeling y-axis
  theme_classic() + # classic theme
  facet_wrap(~Cultivar) # faceted by Cultivar
plot(Plot_2)

```
### Plot 3
```{r}
Plot_3 <- ggplot(Mycotoxin, aes(x = Treatment, y = MassperSeed_mg, color = Cultivar, fill = Cultivar)) +
  geom_boxplot() +
  geom_point(position=position_jitterdodge(dodge.width = 0.6), color = "#009E73") + # coloring points, setting jitter and jitter width
  scale_fill_manual(values=c("#F0E442", "#0072B2")) + # filling and coloring boxplots
  xlab("") + # labeling x-axis
  ylab("Seed Mass (mg)") + # labeling y-axis
  theme_classic() + # classic theme
  facet_wrap(~Cultivar) # faceted by Cultivar
plot(Plot_3)
```
### Combined Plots
```{r}
combined_plot <- ggarrange( # combining the plots
  Plot_1,
  Plot_2,
  Plot_3,
  ncol = 3,
  nrow=1,
  labels = "auto", # labeling the subplots as a, b, and c
  common.legend = TRUE # RESPONSE TO QUESTION 4: common.legend gives all the plots one legend when their keys contain the same items.
  )
plot(combined_plot_t)
```

