---
title: "Coding Challenge 5"
author: "Bria Smith"
date: "2026-03-19"
output:
  pdf_document:
    toc: true
  word_document: null
  md_document:
    variant: gfm
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

Download two .csv files from Canvas called DiversityData.csv and Metadata.csv, and read them into R using relative file paths.

```{r Q1}
library("dplyr")
library("tidyr")
library("ggplot2")
Metadata <- read.csv("Metadata.csv", na.strings="na")
DiversityData <- read.csv("DiversityData.csv", na.strings="na")
```
## Question 2

Join the two dataframes together by the common column ‘Code’. Name the resulting dataframe alpha.

```{r Q2}
alpha<-inner_join(Metadata,DiversityData,by="Code")
str(alpha)
```
## Question 3

Calculate Pielou’s evenness index: Pielou’s evenness is an ecological parameter calculated by the Shannon diversity index (column Shannon) divided by the log of the richness column.

```{r Q3}
alpha$log_Richness <- log(alpha$richness)
alpha_even <- mutate(alpha, Pielou_Evenness = (shannon/(alpha$log_Richness)))
```

## Question 4

Using tidyverse language of functions and the pipe, use the summarise function and tell me the mean and standard error evenness grouped by crop over time.

```{r Q4}
alpha_average <- alpha_even %>%
  group_by(Crop, Time_Point) %>%
  summarise(even.mean = mean(Pielou_Evenness),
            n = n(),
            sd.dev = sd(Pielou_Evenness)) %>%
  mutate(std.err = sd.dev/sqrt(n))
```
## Question 5

Calculate the difference between the soybean column, the soil column, and the difference between the cotton column and the soil column

```{r Q5}
alpha_average2 <- alpha_average %>%
  select(Time_Point,Crop,even.mean) %>%
  pivot_wider(names_from = Crop, values_from = even.mean) %>%
  mutate(diff.cotton.even = Soil-Cotton) %>%
  mutate(diff.soybean.even = Soil-Soybean)

```

## Question 6

Connecting it to plots
```{r Q6}
select(alpha_average2, Time_Point,diff.cotton.even,diff.soybean.even) %>%
pivot_longer(c(diff.cotton.even,diff.soybean.even), names_to = "diff") %>%
ggplot(aes(x=Time_Point, y=value, color = diff)) +
  geom_line() +
  xlab("Time(hrs)") +
  ylab("Difference from soil in Pielou's Evenness")
```

