---
title: "Coding Challenge 6"
author: "Bria Smith"
date: "2026-03-19"
output:  
  pdf_document:
    toc: true
  word_document: null
  md_document:
    variant: gfm
  html_document:
    toc: true
    number_sections: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
[Here is a link to my GitHub!](https://github.com/briacodesinR/briarepository/blob/2a1f65659bc4d32f659fef20f65507a03d831616/PLPA6820_CodingChallenge6.Rmd)
  

## Question 1

Regarding reproducibility, what is the main point of writing your own functions and iterations?

The main point of writing your own functions is to prevent copy-paste errors when repeatedly completing the same function, which also allows data to be more reproducible.

## Question 2

In your own words, describe: 1) how to write a function in R, and 2) how to write a for loop in R. In your answer, be specific about: basic syntax, where the code is written, and how results are returned or stored. 

1) To write a function in R, the function should be defined and the input should be added to the parentheses of the function() function. For the next line, the code required to carry out the task should be added, and return() should be used in the following line to return the result to the console.

2) To complete a for loop in R, the for() function should be used, and an object within a vector or range should be specified in the parentheses. A { is used to define the task being carried out, and a } is used to signal the end of the for loop.

## Question 3
Read in the Cities.csv file from Canvas using a relative file path.
```{r Q3}

Cities <- read.csv("Cities.csv", na.strings="na")

```
## Question 4
Write a function that calculates the distance (in kilometers)
between two pairs of geographic coordinates using the Haversine formula.
```{r Q4}

distance_km <- function(lat1, lon1, lat2, lon2){
  rad.lat1 <- lat1 * pi/180
  rad.lon1 <- lon1 * pi/180
  rad.lat2 <- lat2 * pi/180
  rad.lon2 <- lon2 * pi/180
  delta_lat <- rad.lat2 - rad.lat1
  delta_lon <- rad.lon2 - rad.lon1
  a <- sin(delta_lat/2)^2 + cos(rad.lat1) * cos(rad.lat2) * sin(delta_lon/ 2)^2
  c <- 2 * asin(sqrt(a)) 
  earth_radius <- 6378137
  distance_km <- (earth_radius * c)/1000
  return(distance_km)
}
```

## Question 5
Using your function from question 4, calculate the distance between Auburn, AL and New York City.
```{r Q5}

distance_btwn_AUandNY <- distance_km(lat[1],lon[1],lat[40],lon[40])

```

## Question 6
Use your distance function inside a for loop to calculate the distance between Auburn, AL and every other city in Cities.csv. Each iteration should calculate the distance for one city

```{r}
for (i in 1:39){
  result <- distance_km(lat[i],lon[i],lat[40],lon[40])
  print(result)
}
```

## Question 7
Modify your loop so that each iteration appends one new row to a dataframe with the following columns: City1 (the other city), City2 (Auburn), Distance_km

```{r}
rm(distance.df)
distance.df <- NULL
for (i in 1:40){
  result <- data.frame(distance_km(lat[i],lon[i],lat[40],lon[40]))
  print(result)
  distance.df <- rbind.data.frame(distance.df, result)
  print(distance.df)
}
City1 <- data.frame(Cities$city_ascii)
City2 <- data.frame(Cities$city)
mutate(City1, City2, distance.df)


```

