---
title: "PLPA6820_CodingChallenge4"
author: "Bria Smith"
date: "2026-02-22"
output:
  md_document:
    variant: gfm
  word_document: null
  pdf_document:
    toc: true
  html_document:
    toc: true
    number_sections: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Article from Plant Disease](https://doi.org/10.1094/PDIS-06-21-1253-RE)


[My Repository](https://github.com/briacodesinR/briarepository)


## Question 2a: Explain the following concepts

- YAML Header: gives information on the file title, author, data, and output.My YAML header has my name, shows that I created my R markdown file today, and that it will render as a word document.

- Literate programming: allows individuals to understand the purpose of your code and different steps by combining the programming language with daily language. 

## Question 2b: Read the data using a relative file path
```{r}
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(rmarkdown)
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

Mycotoxin <- read.csv("MycotoxinData.csv", na.strings="na")

```

## Question 2c: Make a separate code chunk for the figures plotting the data
### Plot 1
```{r Plot_1}

Plot_1 <- ggplot(Mycotoxin, aes(x = Treatment, y = DON, color = Cultivar, fill = Cultivar)) +
  geom_boxplot() +
  geom_point(position=position_jitterdodge(dodge.width = 0.6), color = "#009E73") + 
  scale_fill_manual(values=c("#F0E442", "#0072B2")) +
  xlab("") + 
  ylab("DON(ppm)") + 
  theme_classic() + 
  facet_wrap(~Cultivar) 
Mycotoxin$Treatment<- as.factor(Mycotoxin$Treatment)
Mycotoxin$Treatment<- factor(Mycotoxin$Treatment, levels = c("NTC", "Fg", "Fg + 37", "Fg + 40", "Fg + 70")) 
Plot_1t <- Plot_1 +
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}")
plot(Plot_1t)
```

### Plot 2
```{r Plot_2}
Plot_2 <- ggplot(Mycotoxin, aes(x = Treatment, y = X15ADON, color = Cultivar, fill = Cultivar)) +
  geom_boxplot() +
  geom_point(position=position_jitterdodge(dodge.width = 0.6), color = "#009E73") + # coloring points, setting jitter and jitter width
  scale_fill_manual(values=c("#F0E442", "#0072B2")) + # filling and coloring boxplots
  xlab("") + # labeling x-axis
  ylab("15ADON") + # labeling y-axis
  theme_classic() + # classic theme
  facet_wrap(~Cultivar) # faceted by Cultivar
Plot_2t <- Plot_2 +
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}")
plot(Plot_2t)

```

### Plot 3
```{r Plot_3}
Plot_3 <- ggplot(Mycotoxin, aes(x = Treatment, y = MassperSeed_mg, color = Cultivar, fill = Cultivar)) +
  geom_boxplot() +
  geom_point(position=position_jitterdodge(dodge.width = 0.6), color = "#009E73") + # coloring points, setting jitter and jitter width
  scale_fill_manual(values=c("#F0E442", "#0072B2")) + # filling and coloring boxplots
  xlab("") + # labeling x-axis
  ylab("Seed Mass (mg)") + # labeling y-axis
  theme_classic() + # classic theme
  facet_wrap(~Cultivar) # faceted by Cultivar
Plot_3t <- Plot_3 +
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}")
plot(Plot_3t)
```

### Combined Plots
```{r Combined_Plots}
ggarrange( # combining the plots
  Plot_1t,
  Plot_2t,
  Plot_3t,
  ncol = 3,
  nrow=1,
  labels = "auto", # labeling the subplots as a, b, and c
  common.legend = TRUE # RESPONSE TO QUESTION 4: common.legend gives all the plots one legend when their keys contain the same items.
  )

```

