---
title: "Coding Challenge 7"
author: "Bria Smith"
date: "2026-04-01"
output:
  html_document:
    toc: true
  word_document: null
  md_document:
    variant: gfm
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[My Repository for Coding Challenge 7](https://github.com/briacodesinR/briarepository)

install.packages("lme4")
install.packages("emmeans")
install.packages("multcomp")
install.packages("multcompView")


## Question 1
Read in the data called “PlantEmergence.csv” using a relative file path and load the following libraries. tidyverse, lme4, emmeans, multcomp, and multcompView. Turn the Treatment , DaysAfterPlanting and Rep into factors using the function as.factor

```{r Q1}
library(lme4)
library(emmeans)
library(multcomp)
library(tidyverse)
library(multcompView)

PlantEmergence <- read.csv("PlantEmergence.csv", na.string = "na")
PlantEmergence$Treatment <- as.factor(PlantEmergence$Treatment)
PlantEmergence$Rep <- as.factor(PlantEmergence$Rep)
PlantEmergence$DaysAfterPlanting <- as.factor(PlantEmergence$DaysAfterPlanting)
```

## Question 2

Fit a linear model to predict Emergence using Treatment and
DaysAfterPlanting along with the interaction. Provide the summary of the linear model and ANOVA results.

Looking at the summary of the linear model, we can see the intercept and plants using Treatment 2 (p<.001) have significant effects on emergence. There is, however, no significant difference across any of the other variables. Looking at the ANOVA, we see that days after planting (p<.001) and treatment (p<.001) have significant effects on plant emergence. There is no significant difference in the interaction of both variables.

```{r Q2}

lm_model <- lm(Emergence~DaysAfterPlanting*Treatment, data = PlantEmergence)
summary(lm_model)
anova(lm_model)
```

## Question 3
Based on the results of the linear model in question 2, do you need to fit the interaction term? Provide a simplified linear model without the interaction term but still testing both main effects. Provide the summary and ANOVA results. Then, interpret the intercept and the coefficient for Treatment 2.

Based on the results of question 2, we do need to fit the interaction term to better understand the variables outside of the interaction.

Looking at the summary of the linear model, we can see that there is a significant difference in emergence 14, 21, and 28 days after planting. Additionally, we can see that all treatments had a significant effect on emergence except for treatments 4, 7, and 9. In reviewing the ANOVA table, we see that emergence is significantly affected by days since planting (daysafterplanting; p<.001) and treatment received (p<.001).


```{r}
lm_model_q3 <- lm(Emergence~DaysAfterPlanting+Treatment, data = PlantEmergence)
summary(lm_model_q3)
anova(lm_model_q3)

```

## Question 4
Calculate the least square means for Treatment using the emmeans package and perform a Tukey separation with the compact letter display using the cld function.Interpret the results.

From this, we can see that the estimated marginal means of Treatment 2 is lower than all other treatments, although the standard error and df are the same. This contributes to other data demonstrating differences in Treatment 2 when compared to other treatments when considering plant emergence.
```{r}
lsmeans <- emmeans(lm_model_q3, ~Treatment)
result_lsmeans <- cld(lsmeans, alpha = 0.05, reversed = TRUE, details = TRUE)
lsmeans
result_lsmeans
```
## Question 4
The provided function lets you dynamically add a linear model plus one factor from that model and plots a bar chart with letters denoting treatment differences. Use this model to generate the plot shown below. Explain the significance of the letters.

```{r}

```


